---
title: "Supplemental-Info"
output: html_document
---

Working explanatory variables: race and income.
Outcome variable: decision.

Summary statistics

Missingness: 

Total cases involving natural persons: 11461
Total cases with "" and only ascertained decision: 10720
Total cases with "" and NO partial decisions: 9825
Total cases with "" and only ascertained and no missing race: 1304
Total cases with "" and only ascertained and no missing income: 729




Distribution of variables (these plots are also found within the draft)

Number of appellants across racial groups:

```{r}

race_plot <- ggplot(db_npr, 
                             aes(x = appel1_rlabel,
                                 y = (((..count..)/sum(..count..)) * 100))) +
  geom_bar(position = "dodge") +
  labs(x = "Racial Groups", y = "Percent of Appellants") 

race_plot

```

Number of appellants across income levels:

```{r}

income_plot <- ggplot(db_npri, 
                             aes(x = appel1_ilabel,  
                                 y = (((..count..)/sum(..count..)) * 100))) +
  geom_bar(position = "dodge") +
  labs(x = "Income Levels", y = "Percent of Appellants")

income_plot

```

Decisions distributed across racial groups:

```{r}
decision_plot_race <- ggplot(db_npr, 
                             aes(x = appel1_rlabel, 
                                 fill = decision, 
                                 y = (((..count..)/sum(..count..)) * 100))) +
  geom_bar(position = "dodge") +
  labs(x = "Racial Groups", y = "Percent of Appellants") +
  scale_fill_discrete(guide = guide_legend(title = "Decision"))

decision_plot_race
```

Decisions distributed across income levels:

```{r}
decision_plot_income <- ggplot(db_npi, 
                               aes(x = appel1_ilabel, 
                                   fill = decision, 
                                   y = (((..count..)/sum(..count..)) * 100))) +
  geom_bar(position = "dodge") +
  labs(x = "Income Level", y = "Percent of Appellants") +
  scale_fill_discrete(guide = guide_legend(title = "Decision")) 

decision_plot_income
```


